---
title: "EPOC development"
author: "Andrew Constable"
date: "18/05/2020"
output: html_document
---

This markdown document details the development of the EPOC package.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
Universe_data_path```




```{r U_defaul}
# this code runs the default Foosa universe installed with the package

library(EPOC)
# udp = Universe_data_path

udp<-"C:/_w/_r/EPOCdev/EPOCtests/default/data/Universe.data.R"
epoc(udp)

```

Initial call

> epoc(Universe_data_path)
Instantiating model universe using data input file at specified path: C:/_w/_r/EPOCdev/EPOCtests/default/data/Universe.data.R.
Output data files written to: C:/_w/_r/EPOCdev/EPOC/runtime
Error in .local(.Object, ...) : 
  Not compatible with requested type: [type=builtin; target=logical].

Second call
> epoc(Universe_data_path)
Instantiating model universe using data input file at specified path: C:/_w/_r/EPOCdev/EPOCtests/default/data/Universe.data.R.
Output data files written to: C:/_w/_r/EPOCdev/EPOC/runtime
Error in .local(.Object, ...) : 
  long vectors not supported yet: ../include/Rinlinedfuns.h:535
Called from: .local(.Object, ...)
Browse[1]> 


# ERROR: Definition of function '.local' not found
# in namespace 'namespace:EPOC'

